\documentclass[10pt]{article}
\usepackage[a4paper, margin=1in]{geometry}
\usepackage{parskip}
\usepackage{hyperref}

\begin{document}

% Name and contact information
\begin{center}
    {\LARGE \textbf{Ryan Vogel}} \\
    Neptune Beach, Florida \\
    \href{mailto:youremail@example.com}{youremail@example.com} | (Your Phone Number) \\
    \href{https://mandarin3d.com}{mandarin3d.com} | Twitter: @mandarin3d\_
\end{center}

\vspace{0.5cm}
\hrule
\vspace{0.5cm}

% Objective
\textbf{Objective} \\
A driven and creative graphic design major seeking opportunities to apply my skills in branding, packaging design, and logo creation. Dedicated to delivering high-quality work, exceeding expectations, and innovating with a blend of historical and contemporary design influences.

\vspace{0.5cm}

% Education
\textbf{Education} \\
\textbf{University of North Florida}, Bachelor of Fine Arts in Graphic Design \hfill Expected Graduation: [Year] \\
Relevant Coursework: [List Relevant Courses Here]

\vspace{0.5cm}

% Work Experience
\textbf{Work Experience} \\
\textbf{Social Media Manager}, City of Neptune Beach \hfill [Month, Year] -- Present \\
- Manage and create engaging social media content to connect with the Neptune Beach community. \\
- Develop content strategies balancing professional and approachable communication. \\
- Increased social media engagement by [Percentage] through strategic content campaigns.

\textbf{Owner}, Mandarin 3D \hfill [Month, Year] -- Present \\
- Manage a local 3D printing business offering custom printing and design services. \\
- Oversee website design and user experience on \href{https://shop.mandarin3d.com}{shop.mandarin3d.com}. \\
- Create and manage marketing campaigns across Google and Twitter, driving traffic and sales.

\vspace{0.5cm}

% Projects
\textbf{Selected Projects} \\
\textbf{AppliedTrack Web App} \hfill [Year] \\
- Developed a job application tracking app with email discovery and application management features. \\
- Integrated with Hunter.io for effective follow-ups and promoted via social media campaigns.

\textbf{Financial Literacy PSA} \hfill [Year] \\
- Created an 8-slide motion picture PSA to promote financial literacy using a comic-strip style. \\
- Implemented effective storytelling and design principles to convey key financial tips.

\vspace{0.5cm}

% Skills
\textbf{Technical Skills} \\
- \textbf{Graphic Design:} Adobe Creative Suite (Photoshop, Illustrator, InDesign) \\
- \textbf{Web Development:} React, HTML, CSS, JavaScript, Docker, MongoDB, SQL \\
- \textbf{3D Printing:} Bambu Lab P1S, Ankermake M5Cs, Asset Modeling, STL File Management \\
- \textbf{Other:} Social Media Management, Content Strategy, Branding

\vspace{0.5cm}

% Extracurricular Activities
\textbf{Extracurricular Activities} \\
\textbf{Editor in Chief Applicant}, UNF News Program \hfill [Year] \\
- Proposed new initiatives to enhance the program’s reach and content quality.

\textbf{3D Printing Projects} \hfill [Ongoing] \\
- Engaged in various community projects, offering 3D-printed solutions.

\vspace{0.5cm}

% References
\textbf{References} \\
Available upon request.

\end{document}
